Supplemental Material for \\ \textit{Spatial distribution of environmental DNA in a nearshore marine habitat}

### 2017-01-20 Manuscript/v1.2_PeerJ/carkeek_grid.tex
fix caption problems

\usepackage[T1]{fontenc} % Choose an output font encoding (T1) that has support for the accented characters used by the most widespread European languages
\usepackage[utf8]{inputenc} % Allow input of accented characters (and more...)
\usepackage{graphicx} %  figures
\graphicspath{ {../../Figures/} {../Figures/} } % include images in the directory 'Figures' at the same level
\usepackage[round]{natbib} % names in citations
\usepackage{lineno} % line numbers
\usepackage{authblk} % allows more intuitive formatting for multiple authors/affiliations
\usepackage[margin=1in]{geometry} % make the margins 1 inch on all sides of the document
%\usepackage{amsmath} % useful for formatting math stuff, especially complex equations
%\usepackage{pdflscape} % rotate table into landscape mode
%\usepackage{subfigure} % side by side figures
%\usepackage{longtable} % for tables that span multiple pages.
\usepackage{setspace} % double spacing
\usepackage{float} % figure placement [H]
\usepackage{nameref} % named references (e.g. "Supplemental Material")
\usepackage{breakcites} % add line breaks in citations where necessary
\usepackage[breaklinks=true]{hyperref}

@@

%-----------------------------------METHODS-------------------------------------
\section*{Methods}
There are seven discrete steps to our methodology: (1) Environmental sample collection, (2) isolation of particulates from water via filtration, (3) isolation of DNA from filter membrane, (4) amplification of target locus via PCR, (5) sequencing of amplicons, (6) bioinformatic translation of raw sequence data into tables of sequence abundance among samples, and (7) community ecological analyses of eDNA. We provide brief overviews of these steps here, and encourage the reader to review the fully detailed methods presented in the supplementary material (\nameref{supplement}).

@@

\begin{figure}[H] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[width=1\textwidth]{site_map.pdf}
    \caption{\protect\input{"../../Figures/site_map_legend.txt"}}
  \label{site_map}
\end{figure}

\begin{figure}[H] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[width=1\textwidth]{distance_decay.pdf}
    \caption{\protect\input{"../../Figures/distance_decay_legend.txt"}}
  \label{distance_decay}
\end{figure}

\begin{figure}[H] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[width=1\textwidth]{pam_sil.pdf}
    \caption{\protect\input{"../../Figures/pam_sil_legend.txt"}}
  \label{pam_sil}
\end{figure}

\begin{figure}[H] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[width=1\textwidth]{pam_in_space.pdf}
    \caption{\protect\input{"../../Figures/pam_in_space_legend.txt"}}
  \label{pam_in_space}
\end{figure}

\begin{figure}[H] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[width=1\textwidth]{diversity_distance.pdf}
    \caption{\protect\input{"../../Figures/diversity_distance_legend.txt"}}
  \label{diversity_distance}
\end{figure}
\pagebreak

\begin{figure}[H] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[width=1\textwidth]{diversity.pdf}
    \caption{\protect\input{"../../Figures/diversity_legend.txt"}}
  \label{diversity}
\end{figure}

\begin{figure}[H] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[width=1\textwidth]{otu_in_space_select.pdf}
    \caption{\protect\input{"../../Figures/otu_in_space_select_legend.txt"}}
  \label{otu_in_space_select}
\end{figure}

>>>>

\usepackage[T1]{fontenc} % Choose an output font encoding (T1) that has support for the accented characters used by the most widespread European languages
\usepackage[utf8]{inputenc} % Allow input of accented characters (and more...)
\usepackage{graphicx} %  figures
\graphicspath{ {../../Figures/} {../Figures/} } % include images in the directory 'Figures' at the same level
\usepackage[round]{natbib} % names in citations
\usepackage{lineno} % line numbers
\usepackage{authblk} % allows more intuitive formatting for multiple authors/affiliations
\usepackage[margin=1in]{geometry} % make the margins 1 inch on all sides of the document
%\usepackage{amsmath} % useful for formatting math stuff, especially complex equations
%\usepackage{pdflscape} % rotate table into landscape mode
%\usepackage{subfigure} % side by side figures
%\usepackage{longtable} % for tables that span multiple pages.
\usepackage{setspace} % double spacing
\usepackage{float} % figure placement [H]
\usepackage{nameref} % named references (e.g. "Supplemental Material")
\usepackage{breakcites} % add line breaks in citations where necessary
% \usepackage[breaklinks=true]{hyperref}

@@

%-----------------------------------METHODS-------------------------------------
\section*{Methods}
There are seven discrete steps to our methodology: (1) Environmental sample collection, (2) isolation of particulates from water via filtration, (3) isolation of DNA from filter membrane, (4) amplification of target locus via PCR, (5) sequencing of amplicons, (6) bioinformatic translation of raw sequence data into tables of sequence abundance among samples, and (7) community ecological analyses of eDNA. We provide brief overviews of these steps here, and encourage the reader to review the fully detailed methods presented in the supplementary material.

@@

\begin{figure}[H] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[width=1\textwidth]{site_map.pdf}
    \caption{
		Map of study area.
		Depth in meters below sea level is indicated by shading and 25 meter contours. Sampled locations are indicated by red points.
		}
  \label{site_map}
\end{figure}

\newpage
\begin{figure}[H] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[width=1\textwidth]{distance_decay.pdf}
    \caption{
		Distance decay relationship of environmental DNA communities.
		Each point represents the Bray-Curtis similarity of a site sampled along three parallel transects comprising a 3000 by 4000 meter grid. Blue dashed line represents fit of a nonlinear least squares regression (see Methods), and shading denotes the 95\% confidence interval. Boxplot is comparisons within-sample across PCR replicates, separated by a vertical line at zero, where the central line is the median, the box encompasses the interquartile range, and the lines extend to 1.5 times the interquartile range. Boxplot outliers are omitted for clarity.
		}
  \label{distance_decay}
\end{figure}

\begin{figure}[H] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[width=1\textwidth]{pam_sil.pdf}
    \caption{
		Silhouette widths from PAM analysis.
		Points are the width of the PAM silhouette of each sample at each number of clusters (K). Red line is the mean, blue line is the median. Boxes encompass the interquartile range with a line at the median, and the whiskers extend to 1.5 times the interquartile range. Boxplot outliers are omitted for clarity.
		}
		\label{pam_sil}
\end{figure}

\begin{figure}[H] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[width=1\textwidth]{pam_in_space.pdf}
    \caption{
		Cluster membership of sampled sites.
		Distance from onshore starting point is log scaled. Sites are colored and labeled by their assignment to a cluster by PAM analysis for number of clusters (K) chosen based on a priori expectations (A; 2) and mean silhouette width (B; 8).
		}
  \label{pam_in_space}
\end{figure}

\begin{figure}[H] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[width=1\textwidth]{diversity_distance.pdf}
    \caption{
		Aggregate diversity metrics of each site plotted against distance from shore.
		Both Simpson's Index of evenness (A) and richness (B) are shown, and have been computed from the mean abundance of unique DNA sequences found across 4 PCR replicates at each of 24 sites.
		Lines and bands illustrate the fit and 95\% confidence interval of a linear model.
		}
  \label{diversity_distance}
\end{figure}
\pagebreak

\begin{figure}[H] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[width=1\textwidth]{diversity.pdf}
    \caption{
		Aggregate measures of diversity at each sample site.
		Data are rarefied counts of mitochondrial 16S sequences collected from 3 parallel transects in Puget Sound, Washington, USA.
		Evenness (A) is the probability that two sequences drawn at random are different; richness (B) represents the total number of unique sequences from that location.
		}
  \label{diversity}
\end{figure}

\begin{figure}[H] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[width=1\textwidth]{otu_in_space_select.pdf}
    \caption{
		Distribution of eDNA from select taxa.
		Taxa represented are: Embiotocidae (A), Cupolaconcha meroclista (B), Thysanoessa raschii (C), Mytilus (D), Sessilia (E). Circles are colored and scaled by the proportion of that taxon's maximum proportional abundance.
		That is, the largest circle is the same size in each of the panels, and occurs where that taxon contributed the greatest proportional abundance of reads to that sample.
		}
  \label{otu_in_space_select}
\end{figure}

### 2017-01-20 Manuscript/v1.2_PeerJ/supplement.tex
fix caption problems

\begin{figure}[H] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[height=0.6\textheight]{distance_decay_multi.pdf}
    \caption{\protect\input{"../../Figures/distance_decay_multi_legend.txt"}}
  \label{distance_decay_multi}
\end{figure}

\begin{figure}[H] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[height=0.6\textheight]{rarefaction.pdf}
    \caption{\protect\input{"../../Figures/rarefaction_legend.txt"}}
  \label{rarefaction}
\end{figure}

\begin{figure}[H] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[width=1\textwidth]{diversity_distance_all.pdf}
    \caption{\protect\input{"../../Figures/diversity_distance_all_legend.txt"}}
  \label{diversity_distance_all}
\end{figure}

>>>>

\begin{figure}[H] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[height=0.6\textheight]{distance_decay_multi.pdf}
    \caption{
		Distance decay relationship of environmental DNA communities using a variety of models, metrics, and data subsets.
		Each point represents the similarity of a site sampled along three parallel transects comprising a 3000 by 4000 meter grid.
		Each row of plots represents a different data subset indicated in the right margin, including	the final filtered data reported in the main text (a-d), the unfiltered data including all rare OTUs (e-h), log-transformed (log(x+1)) data (i-l),	OTU abundance scaled relative to within-taxon maximum (m-p), and exclusion of OTUs found at only one site (q-t).
		Columns indicate the similarity index used (Bray Curtis or Morisita-Horn) and whether the input was full abundance data or binary (0,1) transformed data.
		Lines and bands illustrate the fit and 95\% confidence interval of both the	main nonlinear model (red, dashed line) and a simple linear model (blue, solid line).
		Results using the Jaccard distance are omitted because of its similarity to Bray-Curtis.
		}
		\label{distance_decay_multi}
\end{figure}

\begin{figure}[H] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[height=0.6\textheight]{rarefaction.pdf}
    \caption{
		Accumulation of OTUs from 24 environmental samples using randomized rarefaction.
		Four replicate PCRs were conducted using DNA each environmental sample and independently sequenced, but these are collapsed here to illustrate a single representation of richness.
		Sample names indicate the position in the sampling grid: south (S), central (C), or north (N), followed by the distance along the transect, in meters (0, 75, 125, 250, 500, 1000, 2000, 4000).
		Vertical line indicates the minimum combined number of sequence reads per sample.
		Horizontal lines indicate OTU richness for each sample at the minimum combined number of sequence reads.
		}
  \label{rarefaction}
\end{figure}

\begin{figure}[H] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[width=1\textwidth]{diversity_distance_all.pdf}
    \caption[]{
		Aggregate diversity metrics of each site plotted against distance from shore.
		Both Simpson's Index (top; A-F) and richness (bottom; G-L) are shown for a variety of data subsets and transformations (left to right: mean (A,G), unfiltered mean (B,H), log(x + 1) transformed (C,I), scaled (D,J), spatially variable (E,K), and taxon clustered (F,L)).
		Lines and bands illustrate the fit and 95\% confidence interval of a linear model.
		See methods text for detailed data descriptions.
		}
  \label{diversity_distance_all}
\end{figure}
